\cvsection{Experience}

\begin{cventries}
  \cventry
    {Graduate Fellow} % Job title
    {Oregon State University} % Organization
    {Corvallis, OR} % Location
    {September 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took over development of CONSTELATION and modified for use at the OSU TRIGA reactor.}
        \item{Developed astronomer package to process CONSTELATION outputs.}
        \item{Designed experiments to validate CONSTELATION using OSU TRIGA reactor.}
        \item{Developed STAR-CCM+ model for designed experiments.}
        \item{Delegated work to undergraduate research assistants.}
        \item{Presented work at conferences.}
      \end{cvitems}
    }


  \cventry
    {HENRI Design Intern} % Job title
    {Idaho National Laboratory} % Organization
    {Idaho Falls, ID} % Location
    {Summer 2019, 2020, and 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Defined physical dimensions, limits, and parameters for the Helium-3 Enhanced Negative Reactivity Insertion (HENRI) prototype for the Transient Reactor Test (TREAT) facility.}
        \item{Developed concept for a helium recovery system to be used with HENRI.}
        \item{Modeled HENRI prototypes in TREAT using MCNP.}
        \item{Processed CFD data into a format to be used by MCNP for HENRI reactivity calculations in TREAT.}
        \item{Proposed design for HENRI experiments in the OSU TRIGA reactor.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Assistant} % Job title
    {Oregon State University School of Nuclear Science and Engineering} % Organization
    {Corvallis, OR} % Location
    {June 2018 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Quality Assurance documents and procedures in a NQA-1 compliant organization.}
        \item{Assembled and maintained experimental facilities.}
        \item{Designed and implemented LabVIEW code for HENRI to display and record test data.}
        \item{Executed tests on HENRI and the Naval Reactor Test Loop (NRTL).}
        %\item{Co-authored paper for NURETH-18 conference.}
        \item{Presented project progress to sponsors.}
      \end{cvitems}
    }

  \cventry
    {Tutor} % Job title
    {Oregon State University Academics for Student Athletes} % Organization
    {Corvallis, OR} % Location
    {January 2017 - January 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored student athletes in math, physics, chemistry, engineering, English, writing, and other subjects.}
        \item{Taught to different learning styles and varying levels of understanding.}
      \end{cvitems}
    }

  \cventry
    {Coach} % Job title
    {Gig Harbor Canoe and Kayak Racing Team} % Organization
    {Gig Harbor, WA} % Location
    {March 2012 - September 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coached team at five National Championship wins, as well as many regional regattas in the US and Canada.}
		\item {Designed workouts for athletes, catered to experience, age, and goals.}
		\item{Supervised up to 30 athletes at any given time.}
      \end{cvitems}
    }

  
\end{cventries}
