\cvsection{Projects}

\begin{cventries}
  \cventry
    {Current Developer}      % Position
    {CONSTELATION}           % Project
    {Oregon State University}% Location
    {June 2022-Present}   % Date
    {
    \begin{cvitems}
        \item{Coupled model for HENRI using STAR-CCM+ and Serpent 2 with Python wrapper.}
        \item{Modified for use in OSU TRIGA reactor.}
        \item{In development: \href{https://github.com/warrenau/CONSTELATION/tree/ostr}{https://github.com/warrenau/CONSTELATION}.}
    \end{cvitems}
    }


  \cventry
    {Creator}                % Position
    {\textit{astronomer}}             % Project
    {Oregon State University}% Location
    {January 2022-Present}   % Date
    {
    \begin{cvitems}
        \item{Software package written in Python to process outputs of coupled model CONSTELATION for HENRI.}
        \item{In development: \href{https://github.com/warrenau/astronomer}{https://github.com/warrenau/astronomer}.}
    \end{cvitems}
    }

  
  \cventry
    {Team Leader} % Empty position
    {XeNRI} % Project
    {Oregon State University} % Empty location
    {2020} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item{A senior design project that supports the HENRI system.}
		\item {Uses xenon-135, instead of helium-3, to characterize the HENRI system using the Oregon State University TRIGA reactor.}
		\item {Won project of the year within the School of Nuclear Science and Engineering.}
		\item{Presented as a member of a Student Design Project Panel with OSU's College of Engineering.}
        \item{More information can be found at the website: \href{https://sites.google.com/oregonstate.edu/xenridesignproject/home}{https://sites.google.com/oregonstate.edu/xenridesignproject/home}.}
      \end{cvitems}
    }


    \cventry
    {Research Assistant} % Empty position
    {HENRI} % Project
    {Oregon State University} % Empty location
    {June 2018 - Present} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Helium-3 Enhanced Negative Reactivity Insertion (HENRI) system for Transient Reactor Test (TREAT) Facility, with out-of-pile prototype built at OSU.}
        \item{Assembled facility and ran experiments.}
        \item{Designed and assembled control panel for instrumentation and control.}
        \item{Developed control software using LabVIEW.}
      \end{cvitems}
    }


\end{cventries}